\chapter{Summary and Outlook} \label{chap:chapter_8}
In this research work, the topic of Context Aware Recommender System (CARS) is explored and studied under the theme of Digital Sales Excellence. CARS use contextual information which the traditional recommender system tend to ignore. The use of contextual information in the recommendation process helps in better modelling of the user preferences and achieve better results. The results from the models implemented validate this claim. \\ \par

Outlook.
Since this work is based on using machine learning models for CARS, it is very important to consider the few aspects related to the data-set used for training the machine learning models. The main data is derived from the past transactions and using this few additional features has been created. Since RTI sports is transforming towards introducing digitization of process in sales and marketing, the current data collection strategy is very basic. Although for this study, the transactional data was sufficient enough to showcase the underlying buying patterns, additional data collected from the different sources such as online web shop would have provided more information about the users. \\ \par
In most of the real-world recommender systems, the combination of different algorithms is used to achieve better results. For e.g. recommender systems trained on explicit and implicit data. However, in this study due to the unavailability of the explicit data, the choice of algorithms was forced to restrict to those which can handle implicit data. The patterns learned are mostly evaluated in offline testing environment. Such pattern may become outdated as users preferences change from time-to-time. Hence, an online continuous learning system, which learns and adjusts the patterns as users interact with the system.\\ \par
The field of recommender system is rapidly evolving. Many researchers are developing new algorithms based on Artificial Neural Network (ANN) which have proved to perform much better than traditional machine learning algorithms. Using ANN for simulating the purchasing behaviour of users and predicting their preference in real-time is a promising research field.


dhl
At the same time, as more data is collected, privacy
concerns may rightly be triggered. In a 2018 study of global chief marketing officers conducted by digital mar- keting and media group Dentsu Aegis Network, a data breach or misuse of consumer data was cited as their No. 1 strategic risk, and they expressed concern that European data protection regulations will make it harder to build direct relationships with consumers